\sysfull

### 2019-06-28 paper/TOSN/coalescing.tex
remove highlights

\begin{figure}
\centering
\includegraphics[width=.8\columnwidth]{figures/dif_cap}
    \caption{\add{Anatomy of \sys coalescing---A snapshot of measured data showing how \sys coalesces static tasks. \sys takes advantage of the guarantee that an energy buffer offers after a reboot: code execution resumes after energy accumulation reaches the operational threshold (a maximum threshold). Thus, \sys starts with a big coalesced task and shrinks it gradually as the risk of a power failure increases. T stands for task code execution and C for commit or power cut.}}
    \label{fig:coal_anatomy}
\end{figure}

@@

\add{
Fig.~\ref{fig:coal_anatomy} shows a real measurement of \sys coalesced tasks. It shows how \sys coalesces aggressively when the execution is just re-started, taking advantage of the full energy buffer, and how it reduces the coalesced task gradually to minimize the risk of significant progress loss when the device fails. The average measured static task size is $\approx$\,0.28\,ms while the commit time (time needed to save the data into the non-volatile memory) averages at  $\approx$\,0.64\,ms. This highlights the importance of coalescing.
}

>>>>

\begin{figure}
\centering
\includegraphics[width=.8\columnwidth]{figures/dif_cap}
    \caption{Anatomy of \sys coalescing---A snapshot of measured data showing how \sys coalesces static tasks. \sys takes advantage of the guarantee that an energy buffer offers after a reboot: code execution resumes after energy accumulation reaches the operational threshold (a maximum threshold). Thus, \sys starts with a big coalesced task and shrinks it gradually as the risk of a power failure increases. T stands for task code execution and C for commit or power cut.}
    \label{fig:coal_anatomy}
\end{figure}

@@

Fig.~\ref{fig:coal_anatomy} shows a real measurement of \sys coalesced tasks. It shows how \sys coalesces aggressively when the execution is just re-started, taking advantage of the full energy buffer, and how it reduces the coalesced task gradually to minimize the risk of significant progress loss when the device fails. The average measured static task size is $\approx$\,0.28\,ms while the commit time (time needed to save the data into the non-volatile memory) averages at  $\approx$\,0.64\,ms. This highlights the importance of coalescing.

### 2019-06-28 paper/TOSN/evaluation.tex
remove highlights

\caption{\add{Comparison of \sys performance running the \textit{sort} application on two different capacitor sizes. We see that \sys optimizes its coalesced task size based on the energy buffer size.
\textbf{Coalesced task} refers to the first coalesced task after a reboot, \textbf{Exp. time} shows the experiment duration, the \textbf{Runs} column lists the number of complete runs of the application during the experiments. \textbf{Run time} is the device collective uptime needed to finish a single iteration of the \textit{sort} application.}
}
\label{tab:dif_cap}
\add{
\begin{minipage}{\columnwidth}
\begin{center}
\begin{tabular}{llllll}
  \toprule
    \textbf{Cap. size} ($\mu\text{f}$)& \textbf{Exp. time} ($s$)& \textbf{Duty cycle} & \textbf{Coalesced task} ($ms$)   & \textbf{Runs} & \textbf{Run time} ($ms$) \\
        \hline
    47                 &1205             & 12.93\%    & 33                        & 85       & 183      \\
    470                &1205             & 12.79\%    & 88                        & 87       & 177 \\
  \bottomrule
\end{tabular}
\end{center}
\end{minipage}  
}
\end{table}%

@@

\paragraph{Benefits of Adaptive Tasks.}
%
We now compare \sys's performance to Alpaca~\cite{alpaca}---a
\emph{non-adaptive} task-based system with tasks fixed at compile-time.
Fig.~\ref{fig:runtime} shows the average execution time of each
application for \sys and Alpaca, \add{normalized to the latter or, when not possible, to one second}.
\sys provides a performance benefit compared to Alpaca for most
applications. \add{For example, it is 54\% faster than Alpaca when executing the \textit{bc} application. In general,}  the speedup is greatest for applications with repeated WAR
dependencies throughout their code, particularly involving arrays
(\textit{dijkstra}, \textit{fft} and \textit{sort}). \sys's VMM
successfully amortizes the overhead of protecting memory that is accessed in
such patterns.  In applications without locality among accesses to protected
variables \sys incurs overhead from memory
virtualization that causes its performance to be comparable to (or worse than)
Alpaca (\textit{ar}, \textit{cuckoo}).

@@

\paragraph{\add{Different Capacitor Sizes}}
\add{
Table~\ref{tab:dif_cap} shows how \sys optimizes its Coalescing task size based on the amount of buffered energy.
We see that \sys scales up its coalesced task size with a bigger energy buffer and vice versa. This allows it to reduce the time-to-completion of the applications. For example, 
the \textit{sort} run-time is reduced from 183\,ms to 177\,ms when the capacitor is changed from 47\,$\mu$F to 470\,$\mu$F. It should be emphasized that a device with a bigger energy buffer suffers less from power failures (but requires longer charging time). However, as has been measured in Fig.~\ref{fig:overallOverheadBreakdown} and explained in Fig.~\ref{fig:coal_anatomy}, the re-execution penalty for the \textit{sort} application is negligible.  
}

>>>>

\caption{Comparison of \sys performance running the \textit{sort} application on two different capacitor sizes. We see that \sys optimizes its coalesced task size based on the energy buffer size.
\textbf{Coalesced task} refers to the first coalesced task after a reboot, \textbf{Exp. time} shows the experiment duration, the \textbf{Runs} column lists the number of complete runs of the application during the experiments. \textbf{Run time} is the device collective uptime needed to finish a single iteration of the \textit{sort} application.}
\label{tab:dif_cap}

\begin{minipage}{\columnwidth}
\begin{center}
\begin{tabular}{llllll}
  \toprule
    \textbf{Cap. size} ($\mu\text{f}$)& \textbf{Exp. time} ($s$)& \textbf{Duty cycle} & \textbf{Coalesced task} ($ms$)   & \textbf{Runs} & \textbf{Run time} ($ms$) \\
        \hline
    47                 &1205             & 12.93\%    & 33                        & 85       & 183      \\
    470                &1205             & 12.79\%    & 88                        & 87       & 177 \\
  \bottomrule
\end{tabular}
\end{center}
\end{minipage}  
\end{table}%

@@

\paragraph{Benefits of Adaptive Tasks.}
%
We now compare \sys's performance to Alpaca~\cite{alpaca}---a
\emph{non-adaptive} task-based system with tasks fixed at compile-time.
Fig.~\ref{fig:runtime} shows the average execution time of each
application for \sys and Alpaca, normalized to the latter or, when not possible, to one second.
\sys provides a performance benefit compared to Alpaca for most
applications. For example, it is 54\% faster than Alpaca when executing the \textit{bc} application. In general, the speedup is greatest for applications with repeated WAR
dependencies throughout their code, particularly involving arrays
(\textit{dijkstra}, \textit{fft} and \textit{sort}). \sys's VMM
successfully amortizes the overhead of protecting memory that is accessed in
such patterns.  In applications without locality among accesses to protected
variables \sys incurs overhead from memory
virtualization that causes its performance to be comparable to (or worse than)
Alpaca (\textit{ar}, \textit{cuckoo}).

@@

\paragraph{Different Capacitor Sizes}
Table~\ref{tab:dif_cap} shows how \sys optimizes its Coalescing task size based on the amount of buffered energy.
We see that \sys scales up its coalesced task size with a bigger energy buffer and vice versa. This allows it to reduce the time-to-completion of the applications. For example, 
the \textit{sort} run-time is reduced from 183\,ms to 177\,ms when the capacitor is changed from 47\,$\mu$F to 470\,$\mu$F. It should be emphasized that a device with a bigger energy buffer suffers less from power failures (but requires longer charging time). However, as has been measured in Fig.~\ref{fig:overallOverheadBreakdown} and explained in Fig.~\ref{fig:coal_anatomy}, the re-execution penalty for the \textit{sort} application is negligible.

### 2019-06-28 paper/TOSN/hwswsetup.tex
remove highlights

\subsection{Experimental Setup}
\label{sec:results_hardware_software}
\add{
We used three different setups to evaluate \sys: 
(i) an RF-powered energy-harvesting device, WISP\,5.1~\cite{wisp5,wisp}, with a fixed capacitor size of 47\,$\mu$F; 
(ii) an MSP-EXP430FR5969 launchpad~\cite{MSP-EXP430FR5969_launchpad} powered by a BQ25570~\cite{BQ25570EVM-206_website} solar power harvester that is connected to an IXYS SLMD121H04L solar cell~\cite{SLMD121H04L_website} for experimenting with different energy buffers; and
(iii) an MSP-EXP430FR5969 launchpad~\cite{MSP-EXP430FR5969_launchpad} that is continuously powered.
}

\add{
Every benchmark used in Section~\ref{sec:evaluation} was run repeatedly on
each platform for a few minutes to ensure capturing a diverse power 
trace. The exact number of iterations depends on the ambient power intensity and the application itself.
In our experiments, the number of complete runs ranges from 4 to 125.
}

>>>>

\subsection{Experimental Setup}
\label{sec:results_hardware_software}
%
We used three different setups to evaluate \sys: 
(i) an RF-powered energy-harvesting device, WISP\,5.1~\cite{wisp5,wisp}, with a fixed capacitor size of 47\,$\mu$F; 
(ii) an MSP-EXP430FR5969 launchpad~\cite{MSP-EXP430FR5969_launchpad} powered by a BQ25570~\cite{BQ25570EVM-206_website} solar power harvester that is connected to an IXYS SLMD121H04L solar cell~\cite{SLMD121H04L_website} for experimenting with different energy buffers; and
(iii) an MSP-EXP430FR5969 launchpad~\cite{MSP-EXP430FR5969_launchpad} that is continuously powered.

Every benchmark used in Section~\ref{sec:evaluation} was run repeatedly on
each platform for a few minutes to ensure capturing a diverse power 
trace. The exact number of iterations depends on the ambient power intensity and the application itself.
In our experiments, the number of complete runs ranges from 4 to 125.
